\documentclass[12pt,letterpaper]{article}

\usepackage{amsmath, amsthm, amssymb, amsfonts}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{natbib}

\theoremstyle{definition}
\newtheorem{dfn}{Definition}

\begin{document}

% The numbers below controls the amount of space between the following sections
\def\shiftdowna{0.32in}  % Adjust for balance
\def\shiftdownb{0.22in}  % Adjust for balance

% Set up the boiler plate at the top of the page

\begin{center}
\textbf{{\large Project Work Statement}}\\


% SPONSOR
\vspace \shiftdowna
\underline {Sponsor}\\ 
\vspace{5pt}
\textbf{{\large The Shanghai Municipal People’s Government}}\\


% TITLE
\vspace \shiftdowna
\textbf{{\large The Transportation and Highway Administration}}


% STUDENTS
\vspace{0.35in}
\vspace \shiftdownb
\underline {Participants} \\
\vspace{5pt}
\text{Jing Huang (Rachel)}, \texttt{jhuang63@jhu.edu}

% SPONSORS
\vspace \shiftdownb
\underline {Potential Participants}\\
\vspace{5pt}
Name Lee, \texttt{nhlee@jhu.edu} \\


% DATE
\vspace \shiftdowna
Date: \today

\end{center}

\vfill  
%Fill page to force following note to bottom
\footnoterule
\noindent \small{Any apparent association of this work to The Shanghai Municipal People’s Government is fictional one, and the sole purpose of this work is a class exercise}

\newpage

\section{Background} 
The Trasportation and Highway Administration of the Shanghai Munivipal Peoples Government is responsible for improving the quality of road and highway facilities, conducting transportation flows and solving the traffic congest. Nowadays, as a typical  modern city which has more than 17 million residents, Shanghai receives more and more attention for its worsing traffic congest. As a newly established department of Shanghai Municipal People's Government, the Transportation and Highway Administration gathers the rich intellectual resources and aims at developing health Transportation Flow Systems. Relys on the platform of Shanghai Government, coordinates with other government department, the Transportation and Highway Administration has evolved into a successful policy constitutor. It's ability to collect, process and analyze massive amount of transportation data allows citizens to enjoy healthier transportation systems and enjoy the fruits of modernity.

\section{Problem Statement}

As we mentioned above, the traffic congest is now an urgent issue to tackle in the city of Shanghai. The policy constitutor puts forward policy-"Traffic Control" to deal with traffic congest and want to know the suitability of this policy. To simplify our problem, we will use the existing "Traffic Control" data of Beijing as the base of making prediction. Besides, we use average speed and single line traffic as the standard variables to evaluate clearness of the roads. Combined the theoretical models and real-world statistical data, find the function between average speed and single line traffic. Noticeable, we will only model for the main roads and highways in main districts for the concern of simplification. It is easy to see from the prediction models, the average speed will raise for more than 30％, the effect of the "Traffic Control" policy is apparent. After further research into the long-term traffic, it is easy to see that the raise in traffic flow is largely caused by the raise in the number of vehicles. So the "Traffic Control" policy is only a temporary solution to the traffic congest, a long-term solution is needed to deal with worsing traffic congest.

The sponsor currently has a limited capability to conduct such statistical research and modeling with existing data, and our task is to provide them with a statistical conslucsion with resonable assumptions.  

\section{Approach}
Given a limited amount of our times, we will assume that extraction of 
tracts from an image is already completed.   
\section{Milestones}
We have the following major deadlines:
\begin{itemize}
    \item Work Statement due date, Sep 28, 2012,
    \item Midterm Presentation due date, Oct 12, 2012,
    \item Progress Report due date, Oct 26, 2012,
    \item Final Presentation due date, Nov 6, 2012,
    \item Final Report due date, Nov 30, 2012.
\end{itemize}

\section{Deliverable}
\subsection{From Team to Sponsor} % (fold)
The following outputs are expected from this project:
\begin{itemize}
    \item The prediction of traffic flow after "Traffic Control" 
    \item The model-based average speed
    \item The comparison between traffic condition with-policy and traffic condition without-policy
    \item The optimized number of vehicles 
    \item The long-term solutions that may slove the traffic congest
\end{itemize}

\subsection{From Sponsor to Team} % (fold)

In order for our project to be of successful one, we will need:
\begin{itemize}
    \item The traffic data of Bejing after the "Traffic Control"
    \item Computing resources
    \item The basic data and condition of Shanghai's main road and highways 
    \item Symposium attendance travel expenses.
\end{itemize}


%\newpage
%\bibliographystyle{plain}
%%\renewcommand\bibname{Selected Bibliography Including Cited Works}
%\nocite{*}
%\bibliography{biblio}

\end{document}
